manuscript_figures

### 2024-06-17 scripts/data_cleaning.Rmd
output master datafrae

# Melt only columns AGH:WHEL into long format
QUAD_long <- QUAD %>%
  pivot_longer(cols = AGH:Oar.Weed.Total, names_to = "SP_CODE", values_to = "COUNT")

)# use rbind.fill() method in R to combine data frames with different columns
QUAD_data <- rbind.fill(QUAD_long, QUAD_2018, FtWeatherill_QUAD_2017, FtWeatherill_QUAD_2016_TALBENHORIN)

>>>>

# Remove last two rows with kelp and oar weed totals
QUAD <- QUAD[ -c(128:130) ]

# Melt only columns AGH:WHEL into long format
QUAD_long <- QUAD %>%
  pivot_longer(cols = AGH:NP, names_to = "SP_CODE", values_to = "COUNT")

# Select only the code and type columns from species.metadata
species_metadata_type <- species.metadata[, c("code", "type")]

# Merge quad_long dataframe with species.metadata to include type information
quad_long_with_type <- merge(QUAD_long, species.metadata[, c("code", "type")], by.x = "SP_CODE", by.y = "code", all.x = TRUE)

# use rbind.fill() method in R to combine data frames with different columns
QUAD_data <- rbind.fill(QUAD_long, QUAD_2018, FtWeatherill_QUAD_2017, FtWeatherill_QUAD_2016_TALBENHORIN)

### 2024-06-17 scripts/manuscript_figures.Rmd
output master datafrae

# Fit the linear mixed effects model
lmm_model <- lmer(mean_fish_biomass ~ mean_kelp_cover + SITE + (1 | SITE/YEAR), data = aggregated_data_cover)
#check normality
qqPlot(residuals(lmm_model)) #slightly non normal values, log transform to improve

@@

# Filter quad data for all inverts and use to correlate to fish biomass
```{r}

@@

@@

>>>>

# Fit the linear mixed effects model
lm_model <- lmer(mean_fish_biomass ~ mean_kelp_cover + SITE + (1 | SITE/YEAR), data = aggregated_data_cover)
#check normality
qqPlot(residuals(lm_model)) #slightly non normal values, log transform to improve

@@

# Filter quad data for all inverts and use to correlate to fish biomass
```{r}
invert.filt <-

@@

# output to .csv
write.csv("output/cleaned_data/mast_output_dataframe.csv")

@@

# Run model on temperature by date between two sites 
```{r}
# Add a 'Site' column to each dataframe
FW_temperature$Site <- "FW"
KB_temperature$Site <- "KB"

# Combine data frames
temperature_data <- rbind(FW_temperature, KB_temperature)

# Run normality on the temp data
qqPlot(temperature_data$Temp, main = "QQ Plot of Temperature Data")

# Data is not normal so log transform
qqPlot(temperature_data$log(Temp), main = "QQ Plot of Temperature Data")

# Fit linear model
lm_model <- lm(log(Temp) ~ Date + Site, data = temperature_data)

# Summary of the model
summary(lm_model)
